$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-11 paper/e6ssm-tuning-paper.tex
Fixed a typo

In general though it is possible for gauge kinetic mixing to be much larger as can be the case if one considers an additional $5 + \overline{5}$ pair of SU(5) multiplets \cite{Rizzo:1998ut} or as has been looked in the $U(1)_{B-L}$ \cite{Salvioni:2009mt,Krauss:2012ku}.  In such a case this will  impact the results in two ways, firstly by altering the $Z^\prime$ limit from experiment and secondly by altering the charges which appear in the EWSB condition, which can be ween from examining Eqs.~\ref{eq:originalE6MZequation}-\ref{eq:ddefn}.

>>>>

In general though it is possible for gauge kinetic mixing to be much larger as can be the case if one considers an additional $5 + \overline{5}$ pair of SU(5) multiplets \cite{Rizzo:1998ut} or as has been looked in the $U(1)_{B-L}$ \cite{Salvioni:2009mt,Krauss:2012ku}.  In such a case this will  impact the results in two ways, firstly by altering the $Z^\prime$ limit from experiment and secondly by altering the charges which appear in the EWSB condition, which can be seen from examining Eqs.~(\ref{eq:originalE6MZequation})-(\ref{eq:ddefn}).
